The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-17 paper.tex
update

  For these two reasons,\
  we have ignored the CR diffusion and the magnetic field throughout\
  the simulation.\
  Also, we do not simulate the spectral evolution of the CR\
  and assume the CR pressure is much less than the gas pressure over the bubbles formation so that\
  the contribution of CR pressure gradient to the momentum of the gas can be ignored.
  In addition, we neglect the cooling and heating processes of CRs,\
  such as energy losses due to synchrotron and inverse Compton emission,\
  and CR reacceleration in shocks/turbulences.

>>>>

  For these two reasons,\
  we have ignored the CR diffusion and the magnetic field throughout\
  the simulation.\
  Also, we do not simulate the spectral evolution of the CR\
  and assume the pressure ratio of CR to gas is much less than 1 over the bubbles formation so that\
  the contribution of CR pressure gradient to the momentum of the gas can be ignored.\
  (We will see that the pressure ratio is around 0.1--0.2 throughtout the bubbles formation)\
  In addition, we neglect the cooling and heating processes of CRs,\
  such as energy losses due to synchrotron and inverse Compton emission,\
  and CR reacceleration in shocks/turbulences.
